Model LF

### 2022-12-10 max_dp endogen stød.Rmd
com

```{r}
###Gengivelse af stød til model
part_bs1 = Shock_bs1$simulation$part
unemp_bs1 = Shock_bs1$simulation$unemp
komp_r_bs1 = Shock_bs1$simulation$komp_r
part_bs1 = Shock_bs1$simulation$part
yk_ds_bs1 = Shock_bs1$simulation$yk_ds
pc_ds_bs1 = Shock_bs1$simulation$pc_ds
wage_ds_t_bs1 = Shock_bs1$simulation$wage_ds_t
ur_ds_bs1 = Shock_bs1$simulation$ur_ds
emp_bs1 = Shock_bs1$simulation$emp
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
pconk_ds_bs1= Shock_bs1$simulation$pconk_ds
tilpas_pr_bs1 = Shock_bs1$simulation$tilpas_pr
u_ds_bs1 = Shock_bs1$simulation$u_ds
part_bs1 = Shock_bs1$simulation$part
nben_h_bs1 = Shock_bs1$simulation$nben_h
wage_ds_bs1 = Shock_bs1$simulation$wage_ds
dp_person_bs1 = Shock_bs1$simulation$dp_person
kont_h_ratio_bs1 = Shock_bs1$simulation$kont_h_ratio
unemp_bs1 = Shock_bs1$simulation$unemp
nl_g_bs1 = Shock_bs1$simulation$nl_g
inflation_bs1 = Shock_bs1$simulation$inflation
lf_bs1 = Shock_bs1$simulation$lf
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
wage_gap1_bs1 = Shock_bs1$simulation$wage_gap1
wage_gap_bs1 = Shock_bs1$simulation$wage_gap
prod_bs1 = Shock_bs1$simulation$prod
prodk_ds_bs1 = Shock_bs1$simulation$prodk_ds

xk_ds_bs1 = Shock_bs1$simulation$xk_ds
mk_ds_bs1 = Shock_bs1$simulation$mk_ds

@@

```{r}
###Gengivelse af stød til model
max_dp_bs2 = Shock_bs2$simulation$max_dp
wage_bs2 = Shock_bs2$simulation$wage
komp_r_bs2 = Shock_bs2$simulation$komp_r
part_bs2 = Shock_bs2$simulation$part
yk_ds_bs2 = Shock_bs2$simulation$yk_ds
pc_ds_bs2 = Shock_bs2$simulation$pc_ds
wage_ds_t_bs2 = Shock_bs2$simulation$wage_ds_t
ur_ds_bs2 = Shock_bs2$simulation$ur_ds
emp_bs2 = Shock_bs2$simulation$emp
yd_hk_ds_bs2 = Shock_bs2$simulation$yd_hk_ds
pconk_ds_bs2= Shock_bs2$simulation$pconk_ds
tilpas_pr_bs2 = Shock_bs2$simulation$tilpas_pr
u_ds_bs2 = Shock_bs2$simulation$u_ds
part_bs2 = Shock_bs2$simulation$part
nben_h_bs2 = Shock_bs2$simulation$nben_h
wage_ds_bs2 = Shock_bs2$simulation$wage_ds
dp_person_bs2 = Shock_bs2$simulation$dp_person
kont_h_ratio_bs2 = Shock_bs2$simulation$kont_h_ratio
unemp_bs2 = Shock_bs2$simulation$unemp
nl_g_bs2 = Shock_bs2$simulation$nl_g
inflation_bs2 = Shock_bs2$simulation$inflation
lf_bs2 = Shock_bs2$simulation$lf
yd_hk_ds_bs2 = Shock_bs2$simulation$yd_hk_ds
wage_gap1_bs2 = Shock_bs2$simulation$wage_gap1
wage_gap_bs2 = Shock_bs2$simulation$wage_gap
prod_bs2 = Shock_bs2$simulation$prod
prod_bs2 = Shock_bs2$simulation$prod
ws_bs2 = Shock_bs2$simulation$ws
xk_ds_bs2 = Shock_bs2$simulation$xk_ds
mk_ds_bs2 = Shock_bs2$simulation$mk_ds

net_balance_bs2 = xk_ds_bs2 - mk_ds_bs2
net_balance_bs2_ratio= (xk_ds_bs2 - mk_ds_bs2)/yk_ds_bs2

ik_bs2 = Shock_bs2$simulation$ik
mk_bs2 = Shock_bs2$simulation$mk

@@

```{r}
###Gengivelse af stød til model
part_000 = Shock_0$simulation$part
unemp_000 = Shock_0$simulation$unemp
komp_r_000 = Shock_0$simulation$komp_r
part_000 = Shock_0$simulation$part
yk_ds_000 = Shock_0$simulation$yk_ds
pc_ds_000 = Shock_0$simulation$pc_ds
wage_ds_t_000 = Shock_0$simulation$wage_ds_t
ur_ds_000 = Shock_0$simulation$ur_ds
emp_000 = Shock_0$simulation$emp
yd_hk_ds_000 = Shock_0$simulation$yd_hk_ds
lf_000 = Shock_0$simulation$lf
tilpas_pr_000 = Shock_0$simulation$tilpas_pr
u_ds_000 = Shock_0$simulation$u_ds
part_000 = Shock_0$simulation$part
nben_h_000 = Shock_0$simulation$nben_h
wage_ds_000 = Shock_0$simulation$wage_ds
dp_person_000 = Shock_0$simulation$dp_person
kont_h_ratio_000 = Shock_0$simulation$kont_h_ratio

nl_g_000 = Shock_0$simulation$nl_g
prodk_ds_000 = Shock_0$simulation$prodk_ds
yd_hk_ds_000 = Shock_0$simulation$yd_hk_ds
wage_gap1_000 = Shock_0$simulation$wage_gap1
wage_gap_000 = Shock_0$simulation$wage_gap
prod_000 = Shock_0$simulation$prod
```

@@

```{r}
plot((emp_000-emp_bs1)*1000, col= "red");
```

@@

```{r}
###Gengivelse af stød til model
max_dp_01 = Shock_1$simulation$max_dp
wage_01 = Shock_1$simulation$wage
komp_r_01 = Shock_1$simulation$komp_r
part_01 = Shock_1$simulation$part
yk_ds_01 = Shock_1$simulation$yk_ds
pc_ds_01 = Shock_1$simulation$pc_ds
wage_ds_t_01 = Shock_1$simulation$wage_ds_t
ur_ds_01 = Shock_1$simulation$ur_ds
emp_01 = Shock_1$simulation$emp
yd_hk_ds_01 = Shock_1$simulation$yd_hk_ds

tilpas_pr_01 = Shock_1$simulation$tilpas_pr
u_ds_01 = Shock_1$simulation$u_ds
part_01 = Shock_1$simulation$part
nben_h_01 = Shock_1$simulation$nben_h
wage_ds_01 = Shock_1$simulation$wage_ds
dp_person_01 = Shock_1$simulation$dp_person
kont_h_ratio_01 = Shock_1$simulation$kont_h_ratio

nl_g_01 = Shock_1$simulation$nl_g
unemp_01 = Shock_1$simulation$unemp
yd_hk_ds_01 = Shock_1$simulation$yd_hk_ds
wage_gap1_01 = Shock_1$simulation$wage_gap1
wage_gap_01 = Shock_1$simulation$wage_gap
prod_01 = Shock_1$simulation$prod
```

@@

yk_ds_02 = Shock_2$simulation$yk_ds
emp_02 = Shock_2$simulation$emp
wage_ds_02 = Shock_2$simulation$wage_ds
ur_ds_02 = Shock_2$simulation$ur_ds
pc_ds_02 = Shock_2$simulation$pc_ds
yd_hk_ds_02 = Shock_2$simulation$yd_hk_ds
pconk_ds_02 = Shock_2$simulation$pconk_ds
komp_r_02 = Shock_2$simulation$komp_r
max_dp_02 = Shock_2$simulation$max_dp
nben_h_02 = Shock_2$simulation$nben_h
yd_hk_ds_02 = Shock_2$simulation$yd_hk_ds
ik_02 = Shock_2$simulation$ik
wage_ds_t_02 = Shock_2$simulation$wage_ds_t
nben_h_un_02 = Shock_2$simulation$nben_h_un
nl_g_02 = Shock_2$simulation$nl_g
nsben_h_02 = Shock_2$simulation$nsben_h
dp_person_02 = Shock_2$simulation$dp_person
xk_ds_02 = Shock_2$simulation$xk_ds
mk_ds_02 = Shock_2$simulation$mk_ds
ik_02 = Shock_2$simulation$ik
rer_02 = Shock_2$simulation$rer
ps_ds_02 = Shock_2$simulation$ps_ds
i_bd_nfc_k_ds_02 = Shock_2$simulation$i_bd_nfc_k_ds
yd1_hk_ds_02 = Shock_2$simulation$yd1_hk_ds
yd2a_hk_ds_02 = Shock_2$simulation$yd2a_hk_ds
yd2b_hk_02 = Shock_2$simulation$yd2b_hk
i_equip_nfc_k_ds_02 = Shock_2$simulation$i_equip_nfc_k_ds
u_ds_02 = Shock_2$simulation$u_ds
wage_gap1_02 = Shock_2$simulation$wage_gap1
gk_02 = Shock_2$simulation$gk
kont_h_ratio_02 = Shock_2$simulation$kont_h_ratio
lf_02 = Shock_2$simulation$lf
wage_gap_02 = Shock_2$simulation$wage_gap
max_gap_02 = Shock_2$simulation$max_gap
unemp_02 = Shock_2$simulation$unemp
inflation_02 = Shock_2$simulation$inflation
prod_02 = Shock_2$simulation$prod
ws_02 = Shock_2$simulation$ws
net_balance_02 = xk_ds_02 - mk_ds_02
```

@@

yk_ds_07b = Shock_7b$simulation$yk_ds
emp_07b = Shock_7b$simulation$emp
wage_ds_07b= Shock_7b$simulation$wage_ds
ur_ds_07b = Shock_7b$simulation$ur_ds
pc_ds_07b = Shock_7b$simulation$pc_ds
yd_hk_ds_07b = Shock_7b$simulation$yd_hk_ds
pconk_ds_07b = Shock_7b$simulation$pconk_ds
komp_r_07b = Shock_7b$simulation$komp_r
max_dp_07b = Shock_7b$simulation$max_dp
nben_h_07b = Shock_7b$simulation$nben_h
yd_hk_ds_07b = Shock_7b$simulation$yd_hk_ds
ik_07b = Shock_7b$simulation$ik
wage_ds_t_07b = Shock_7b$simulation$wage_ds_t
nben_h_un_07b = Shock_7b$simulation$nben_h_un
nl_g_07b = Shock_7b$simulation$nl_g
nsben_h_07b = Shock_7b$simulation$nsben_h
dp_person_07b = Shock_7b$simulation$dp_person
u_ds_07b = Shock_7b$simulation$u_ds
shock_kuld_07b = Shock_7b$simulation$shock_kuld
unemp_07b = Shock_7b$simulation$unemp
lf_07b = Shock_7b$simulation$lf
part_07b = Shock_7b$simulation$part
yk_07b = Shock_7b$simulation$yk
y_07b = Shock_7b$simulation$y
prodk_07b = Shock_7b$simulation$prodk

y_yk_07b=yk_07b/y_07b
```

@@

>>>>

```{r}
###Gengivelse af stød til model
part_bs1 = Shock_bs1$simulation$part
unemp_bs1 = Shock_bs1$simulation$unemp
komp_r_bs1 = Shock_bs1$simulation$komp_r
part_bs1 = Shock_bs1$simulation$part
yk_ds_bs1 = Shock_bs1$simulation$yk_ds
pc_ds_bs1 = Shock_bs1$simulation$pc_ds
wage_ds_t_bs1 = Shock_bs1$simulation$wage_ds_t
ur_ds_bs1 = Shock_bs1$simulation$ur_ds
emp_bs1 = Shock_bs1$simulation$emp
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
pconk_ds_bs1= Shock_bs1$simulation$pconk_ds
tilpas_pr_bs1 = Shock_bs1$simulation$tilpas_pr
u_ds_bs1 = Shock_bs1$simulation$u_ds
part_bs1 = Shock_bs1$simulation$part
nben_h_bs1 = Shock_bs1$simulation$nben_h
wage_ds_bs1 = Shock_bs1$simulation$wage_ds
dp_person_bs1 = Shock_bs1$simulation$dp_person
kont_h_ratio_bs1 = Shock_bs1$simulation$kont_h_ratio
unemp_bs1 = Shock_bs1$simulation$unemp
nl_g_bs1 = Shock_bs1$simulation$nl_g
inflation_bs1 = Shock_bs1$simulation$inflation
lf_bs1 = Shock_bs1$simulation$lf
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
wage_gap1_bs1 = Shock_bs1$simulation$wage_gap1
wage_gap_bs1 = Shock_bs1$simulation$wage_gap
prod_bs1 = Shock_bs1$simulation$prod
prodk_ds_bs1 = Shock_bs1$simulation$prodk_ds
ur_bs1 = Shock_bs1$simulation$ur
xk_ds_bs1 = Shock_bs1$simulation$xk_ds
mk_ds_bs1 = Shock_bs1$simulation$mk_ds

@@

```{r}
###Gengivelse af stød til model
max_dp_bs2 = Shock_bs2$simulation$max_dp
wage_bs2 = Shock_bs2$simulation$wage
komp_r_bs2 = Shock_bs2$simulation$komp_r
part_bs2 = Shock_bs2$simulation$part
yk_ds_bs2 = Shock_bs2$simulation$yk_ds
yk_bs2 = Shock_bs2$simulation$yk
pc_ds_bs2 = Shock_bs2$simulation$pc_ds
wage_ds_t_bs2 = Shock_bs2$simulation$wage_ds_t
ur_ds_bs2 = Shock_bs2$simulation$ur_ds
emp_bs2 = Shock_bs2$simulation$emp
yd_hk_ds_bs2 = Shock_bs2$simulation$yd_hk_ds
pconk_ds_bs2= Shock_bs2$simulation$pconk_ds
tilpas_pr_bs2 = Shock_bs2$simulation$tilpas_pr
u_ds_bs2 = Shock_bs2$simulation$u_ds
part_bs2 = Shock_bs2$simulation$part
nben_h_bs2 = Shock_bs2$simulation$nben_h
wage_ds_bs2 = Shock_bs2$simulation$wage_ds
dp_person_bs2 = Shock_bs2$simulation$dp_person
kont_h_ratio_bs2 = Shock_bs2$simulation$kont_h_ratio
unemp_bs2 = Shock_bs2$simulation$unemp
nl_g_bs2 = Shock_bs2$simulation$nl_g
inflation_bs2 = Shock_bs2$simulation$inflation
lf_bs2 = Shock_bs2$simulation$lf
yd_hk_ds_bs2 = Shock_bs2$simulation$yd_hk_ds
wage_gap1_bs2 = Shock_bs2$simulation$wage_gap1
wage_gap_bs2 = Shock_bs2$simulation$wage_gap
prod_bs2 = Shock_bs2$simulation$prod
prod_bs2 = Shock_bs2$simulation$prod
ws_bs2 = Shock_bs2$simulation$ws
xk_ds_bs2 = Shock_bs2$simulation$xk_ds
mk_ds_bs2 = Shock_bs2$simulation$mk_ds
ur_bs2 = Shock_bs2$simulation$ur
net_balance_bs2 = xk_ds_bs2 - mk_ds_bs2
net_balance_bs2_ratio= (xk_ds_bs2 - mk_ds_bs2)/yk_ds_bs2
y_bs2 = Shock_bs2$simulation$y
ik_bs2 = Shock_bs2$simulation$ik
mk_bs2 = Shock_bs2$simulation$mk

@@

```{r}
###Gengivelse af stød til model
part_000 = Shock_0$simulation$part
unemp_000 = Shock_0$simulation$unemp
komp_r_000 = Shock_0$simulation$komp_r
part_000 = Shock_0$simulation$part
yk_ds_000 = Shock_0$simulation$yk_ds
pc_ds_000 = Shock_0$simulation$pc_ds
wage_ds_t_000 = Shock_0$simulation$wage_ds_t
ur_ds_000 = Shock_0$simulation$ur_ds
emp_000 = Shock_0$simulation$emp
yd_hk_ds_000 = Shock_0$simulation$yd_hk_ds
lf_000 = Shock_0$simulation$lf
tilpas_pr_000 = Shock_0$simulation$tilpas_pr
u_ds_000 = Shock_0$simulation$u_ds
part_000 = Shock_0$simulation$part
nben_h_000 = Shock_0$simulation$nben_h
wage_ds_000 = Shock_0$simulation$wage_ds
dp_person_000 = Shock_0$simulation$dp_person
kont_h_ratio_000 = Shock_0$simulation$kont_h_ratio
ur_000 = Shock_0$simulation$ur
nl_g_000 = Shock_0$simulation$nl_g
prodk_ds_000 = Shock_0$simulation$prodk_ds
yd_hk_ds_000 = Shock_0$simulation$yd_hk_ds
wage_gap1_000 = Shock_0$simulation$wage_gap1
wage_gap_000 = Shock_0$simulation$wage_gap
prod_000 = Shock_0$simulation$prod
```

@@

```{r, fig.width=10, fig.height=10}
par(mfrow=c(2,2))

plot((emp_000-emp_bs1)*1000, col= "black", ylim= c(0,250));
lines((emp_01- emp_00)*1000, col="red")

plot((unemp_000-unemp_bs1)*1000, col= "black", ylim= c(-250,0));
lines((unemp_01- unemp_00)*1000, col="red")

plot((wage_ds_000-wage_ds_bs1), col= "black", ylim=c(-0.1,0.1));
lines((wage_ds_01- wage_ds_00), col="red")

plot((ur_000 - ur_bs1), col= "black", xlab= "Year", ylab= "% Change in gdp");
lines(ur_01- ur_00, col="red");
legend("top", legend=c("GDP"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()
```

```{r}
plot((yk_ds_000 - yk_ds_bs1), col= "black", xlab= "Year", ylab= "% Change in gdp");
lines(yk_ds_01- yk_ds_00, col="red");
legend("top", legend=c("GDP"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()
```

@@

```{r}
###Gengivelse af stød til model
max_dp_01 = Shock_1$simulation$max_dp
wage_01 = Shock_1$simulation$wage
komp_r_01 = Shock_1$simulation$komp_r
part_01 = Shock_1$simulation$part
yk_ds_01 = Shock_1$simulation$yk_ds
pc_ds_01 = Shock_1$simulation$pc_ds
wage_ds_t_01 = Shock_1$simulation$wage_ds_t
ur_ds_01 = Shock_1$simulation$ur_ds
emp_01 = Shock_1$simulation$emp
yd_hk_ds_01 = Shock_1$simulation$yd_hk_ds
ur_01 = Shock_1$simulation$ur
tilpas_pr_01 = Shock_1$simulation$tilpas_pr
u_ds_01 = Shock_1$simulation$u_ds
part_01 = Shock_1$simulation$part
nben_h_01 = Shock_1$simulation$nben_h
wage_ds_01 = Shock_1$simulation$wage_ds
dp_person_01 = Shock_1$simulation$dp_person
kont_h_ratio_01 = Shock_1$simulation$kont_h_ratio
lf_01 = Shock_1$simulation$lf
nl_g_01 = Shock_1$simulation$nl_g
unemp_01 = Shock_1$simulation$unemp
yd_hk_ds_01 = Shock_1$simulation$yd_hk_ds
wage_gap1_01 = Shock_1$simulation$wage_gap1
wage_gap_01 = Shock_1$simulation$wage_gap
prod_01 = Shock_1$simulation$prod
```

@@

```{r}
###Gengivelse af stød til model
y_02 = Shock_2$simulation$y
yk_ds_02 = Shock_2$simulation$yk_ds
emp_02 = Shock_2$simulation$emp
wage_ds_02 = Shock_2$simulation$wage_ds
ur_ds_02 = Shock_2$simulation$ur_ds
pc_ds_02 = Shock_2$simulation$pc_ds
yd_hk_ds_02 = Shock_2$simulation$yd_hk_ds
pconk_ds_02 = Shock_2$simulation$pconk_ds
komp_r_02 = Shock_2$simulation$komp_r
max_dp_02 = Shock_2$simulation$max_dp
nben_h_02 = Shock_2$simulation$nben_h
yd_hk_ds_02 = Shock_2$simulation$yd_hk_ds
ik_02 = Shock_2$simulation$ik
wage_ds_t_02 = Shock_2$simulation$wage_ds_t
nben_h_un_02 = Shock_2$simulation$nben_h_un
nl_g_02 = Shock_2$simulation$nl_g
nsben_h_02 = Shock_2$simulation$nsben_h
dp_person_02 = Shock_2$simulation$dp_person
xk_ds_02 = Shock_2$simulation$xk_ds
mk_ds_02 = Shock_2$simulation$mk_ds
ik_02 = Shock_2$simulation$ik
rer_02 = Shock_2$simulation$rer
ps_ds_02 = Shock_2$simulation$ps_ds
i_bd_nfc_k_ds_02 = Shock_2$simulation$i_bd_nfc_k_ds
yd1_hk_ds_02 = Shock_2$simulation$yd1_hk_ds
yd2a_hk_ds_02 = Shock_2$simulation$yd2a_hk_ds
yd2b_hk_02 = Shock_2$simulation$yd2b_hk
i_equip_nfc_k_ds_02 = Shock_2$simulation$i_equip_nfc_k_ds
u_ds_02 = Shock_2$simulation$u_ds
wage_gap1_02 = Shock_2$simulation$wage_gap1
gk_02 = Shock_2$simulation$gk
kont_h_ratio_02 = Shock_2$simulation$kont_h_ratio
lf_02 = Shock_2$simulation$lf
wage_gap_02 = Shock_2$simulation$wage_gap
max_gap_02 = Shock_2$simulation$max_gap
unemp_02 = Shock_2$simulation$unemp
inflation_02 = Shock_2$simulation$inflation
prod_02 = Shock_2$simulation$prod
ws_02 = Shock_2$simulation$ws
net_balance_02 = xk_ds_02 - mk_ds_02
ur_02 = Shock_2$simulation$ur
yk_02 = Shock_2$simulation$yk
```

@@

yk_ds_07b = Shock_7b$simulation$yk_ds
emp_07b = Shock_7b$simulation$emp
wage_ds_07b= Shock_7b$simulation$wage_ds
ur_ds_07b = Shock_7b$simulation$ur_ds
pc_ds_07b = Shock_7b$simulation$pc_ds
yd_hk_ds_07b = Shock_7b$simulation$yd_hk_ds
pconk_ds_07b = Shock_7b$simulation$pconk_ds
komp_r_07b = Shock_7b$simulation$komp_r
max_dp_07b = Shock_7b$simulation$max_dp
nben_h_07b = Shock_7b$simulation$nben_h
yd_hk_ds_07b = Shock_7b$simulation$yd_hk_ds
ik_07b = Shock_7b$simulation$ik
wage_ds_t_07b = Shock_7b$simulation$wage_ds_t
nben_h_un_07b = Shock_7b$simulation$nben_h_un
nl_g_07b = Shock_7b$simulation$nl_g
nsben_h_07b = Shock_7b$simulation$nsben_h
dp_person_07b = Shock_7b$simulation$dp_person
u_ds_07b = Shock_7b$simulation$u_ds
shock_kuld_07b = Shock_7b$simulation$shock_kuld
unemp_07b = Shock_7b$simulation$unemp
lf_07b = Shock_7b$simulation$lf
part_07b = Shock_7b$simulation$part
yk_07b = Shock_7b$simulation$yk
y_07b = Shock_7b$simulation$y
prodk_07b = Shock_7b$simulation$prodk
prod_07b = Shock_7b$simulation$prod
ur_07b = Shock_7b$simulation$ur
y_yk_07b=yk_07b/y_07b
```

@@

```{r}
plot(((wage_ds_02 - wage_ds_bs2)), col= "blue", xlab= "Year", ylab= "Change in unemployment (people)", main= "Sensitivity of Unemployment", ylim=c(0,3));
lines(((wage_ds_07b - wage_ds_bs7b)), col= "red");
grid()

plot(((lf_02 - lf_bs2)), col= "blue", xlab= "Year", ylab= "Change in unemployment (people)", main= "Sensitivity of Unemployment");
lines(((lf_07b - lf_bs7b)), col= "red");
grid()
```

```{r, fig.width=10, fig.height=10}
par(mfrow=c(2,2))

plot((ur_07b-ur_bs7b)*1000, col= "black");
lines((ur_02- ur_bs2)*1000, col="red")

plot((unemp_07b-unemp_bs7b)*1000, col= "black");
lines((unemp_02- unemp_bs2)*1000, col="red")

plot((wage_ds_07b-wage_ds_bs7b), col= "black");
lines((wage_ds_02- wage_ds_bs2), col="red")

plot((prod_07b -prod_bs7b), col= "black", xlab= "Year", ylab= "Ur");
lines(prod_02- prod_bs2, col="red");
legend("top", legend=c("GDP"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()

```{r}
par(mfrow=c(1,2))
plot((y_07b -y_bs7b), col= "black", xlab= "Year", ylab= "Ur");
lines(y_02- y_bs2, col="red");
legend("top", legend=c("GDP"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()

plot((yk_07b -yk_bs7b), col= "black", xlab= "Year", ylab= "Ur");
lines(yk_02- yk_bs2, col="red");
legend("top", legend=c("GDP"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()
```
